SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-06 scipy-1.0/paper.tex
removing comma; clause on right is not independent

The (currently) 18 member Steering Council is chaired by Ralf Gommers and
performs a number of tasks including nominating and voting on new Council
Members, and actively contributing to the progress of the project (could be
code review but also outreach activities, etc.). Generally, one year of sustained
and substantial contributions (not restricted to source code contributions)
that improve the project are the prerequisites for nomination of new Council
Members. Council Members do not get special treatment for the vast majority of
the day to day project activities (code submission / review), though it is
anticipated that their experience with the project will serve as helpful
guidance in many matters.  Council Members have commit rights to the project,
but will typically only incorporate changes when there are no substantive
community objections. The Chair of the Steering Council is responsible for
starting more formal technical reviews of the direction of the project,
ensuring that the composition of the Council remains current, and communicating
/ summarizing any Council activities performed privately to the broader
community. We also describe in some detail how institutional partners may
contribute to the project, but no financial weight from grants or other sources
may be leveraged to circumvent or overrule the technical direction of the
project decided upon by the Steering Committee. The Chair does not have a fixed
term, but is nominated by the Steering Committee and is expected to yield to
substantive claims that stepping down is the appropriate action.

>>>>

The (currently) 18 member Steering Council is chaired by Ralf Gommers and
performs a number of tasks including nominating and voting on new Council
Members, and actively contributing to the progress of the project (could be
code review but also outreach activities, etc.). Generally, one year of sustained
and substantial contributions (not restricted to source code contributions)
that improve the project are the prerequisites for nomination of new Council
Members. Council Members do not get special treatment for the vast majority of
the day to day project activities (code submission / review), though it is
anticipated that their experience with the project will serve as helpful
guidance in many matters.  Council Members have commit rights to the project,
but will typically only incorporate changes when there are no substantive
community objections. The Chair of the Steering Council is responsible for
starting more formal technical reviews of the direction of the project,
ensuring that the composition of the Council remains current, and communicating
/ summarizing any Council activities performed privately to the broader
community. We also describe in some detail how institutional partners may
contribute to the project, but no financial weight from grants or other sources
may be leveraged to circumvent or overrule the technical direction of the
project decided upon by the Steering Committee. The Chair does not have a fixed
term but is nominated by the Steering Committee and is expected to yield to
substantive claims that stepping down is the appropriate action.
